Computational tools for representation theory of affine Lie algebras

### 2009-05-26 AffineLieAlgebras/ACMS2009/article.tex
Some additions on folding

We use the formula (\ref{eq:2}). The summation in the first term of
right-hand side goes through the set of weights $\{\xi+\pi-\omega
\rho\;|\;\omega\in W\backslash e\}$

>>>>

We use the formula (\ref{eq:2}). The summation in the first term of
right-hand side goes through the set of weights $\{\xi+\pi-\omega
\rho\;|\;\omega\in W\backslash e\}$.
But for each weight $\zeta$ outside the main Weyl chamber there exists
weight $\zeta_0$ in main Weyl chamber and $\omega\in W$ such that
$\zeta=\omega \zeta_0$. So to calculate the multiplicity of $\xi$ we
sum over the set of weights inside the main Weyl chamber.

The question is if it is possible to introduce the same procedure for
computation of branching coefficients.
